\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}{\bfseries}{}{0em}{}

\begin{document}
	\pagestyle{empty}
	
	\begin{center}
		{\LARGE \textbf{RAJU UDUTHA}} \\
		Siddipet, Telangana \\
		\href{mailto:rajuudutha1221@gmail.com}{rajuudutha1221@gmail.com} | 
		\href{https://linkedin.com/in/raju-udutha-500879262}{linkedin.com/in/raju-udutha-500879262} | (+91) 9963965964
	\end{center}
	
	\section*{Education}
	\textbf{Rajiv Gandhi University of Knowledge Technologies} \hfill 2022 - Present \\
	Bachelor’s of Technology in Computer Science Engineering \hfill CGPA: 8.56
	
	\section*{Career Objective}
	Aspiring web developer skilled in React, PHP, and MySQL, with a portfolio of dynamic projects. A quick learner passionate about creating efficient, user-friendly applications, seeking an internship to contribute skills, gain industry experience, and grow as a developer.
	
	\section*{Projects}
	\textbf{Farmer-Retailer Connect} \\
	Developing a platform for direct farmer-retailer interactions with location-based farmer suggestions, using React, PHP, and MySQL. Currently learning backend development, API integration, and further enhancing my skills in these technologies.
	
	\textbf{Email Software} \\
	Built a web-based email client with features like login, inbox viewing, and message composing, using JSP for authentication, email handling, and dynamic updates. Gained practical experience in JSP, HTML, CSS, and JavaScript.
	
	\textbf{RGUKT Interface} \\
	Developed a responsive RGUKT website using HTML, CSS, and JavaScript, integrating interactive features and optimized navigation for a better user experience. Gained expertise in responsive design and front-end development tools.
	
	\section*{Technical Strengths}
	\textbf{Languages:} HTML, CSS, JavaScript, Python, C, C++, Java, PHP \\
	\textbf{Database:} MySQL, MongoDB \\
	\textbf{Tools:} Git, GitHub, VS Code \\
	\textbf{Libraries/Frameworks:} React.js, pandas, NumPy, Matplotlib \\
	\textbf{Soft Skills:} Communication, Problem Solving, Leadership, Time Management, Adaptability
	
	\section*{Accomplishments}
	Proficient in solving coding challenges on platforms like GeeksforGeeks and LeetCode, with a focus on algorithms, data structures, and SQL.
	
	\section*{Volunteer Experience}
	\textbf{Web Camera Agent} \\
	Ensured smooth operation of web cameras for live election monitoring, coordinated with the technical team to resolve issues, and contributed to accurate data collection for transparency. Assisted colleagues with technical tasks and on-site challenges.
	
	\section*{Leadership Experience}
	\textbf{School Leader} \\
	Led educational programs, supported faculty development, and collaborated with students, teachers, and parents to resolve issues. Organized events to boost student engagement and managed teams to ensure efficient operations, enhancing leadership and organizational abilities.
	
\end{document}
